How does an Experimental Software Engineering Lab Work? An Ethnographic Study

### 2023-07-24 tex/research-method.tex
Last changes
Last changes  made before the submission.

\begin{table*}
	\small
	\centering
	\caption{Techniques and tools for information acquisition, by source}
	\label{tbl-tecnica-fuente}
	\begin{tabular}{|p{2cm}|p{3.5cm}|p{5cm}|}
	\hline
	\textbf{Source} & \textbf{Technique} & \textbf{Instruments}\\
	\hline
	\multirow{7}{50 pt}{Experimenters knowledge} & Interviews & Video camera, paper, pencil\\
	\cline{2-2}\cline{3-3}
	& Focus groups & Video camera, blackboard, cardboard, board markers, chalkboard eraser, etc.\\
	\cline{2-2}\cline{3-3}
	& Process modeling & Video camera, paper, pencil\\
	\cline{2-2}\cline{3-3}
	& Instrumental systems & Email, videoconferences, internet\\
	\cline{2-2}\cline{3-3}
	& Experience-based learning & Literature review, review of experimental material, experimentation in practice\\
	\hline
	\multirow{3}{15 pt}{Common literature} & Documentation analysis & Comprehensive reading of literature, reading summaries, software support tools\\
	\hline
	\multirow{2}{15 pt}{Experimental material} & Documentation analysis & Systematic analysis of experimental material, trials with data\\
	\hline
	\multirow{2}{15 pt}{Group activities} & Participatory observation & Literature review, researchers knowledge\\
	\hline
	\end{tabular}
\end{table*}

>>>>

\begin{table}
	\small
	\centering
	\caption{Techniques and tools for information acquisition, by source}
	\label{tbl-tecnica-fuente}
	\begin{tabular}{|p{2cm}|p{2.5cm}|p{3cm}|}
	\hline
	\textbf{Source} & \textbf{Technique} & \textbf{Instruments}\\
	\hline
	\multirow{14}{50 pt}{Experimenters knowledge} & Interviews & Video camera, paper, pencil\\
	\cmidrule{2-2}\cmidrule{3-3}
	& Focus groups & Video camera, blackboard, cardboard, board markers, chalkboard eraser, etc.\\
	\cmidrule{2-2}\cmidrule{3-3}
	& Process modeling & Video camera, paper, pencil\\
	\cmidrule{2-2}\cmidrule{3-3}
	& Instrumental systems & Email, videoconferences, internet\\
	\cmidrule{2-2}\cmidrule{3-3}
	& Experience-based learning & Literature review, review of experimental material, experimentation in practice\\
	\hline
	\multirow{4}{15 pt}{Common literature} & Documentation analysis & Comprehensive reading of literature, reading summaries, software support tools\\
	\hline
	\multirow{3}{15 pt}{Experimental material} & Documentation analysis & Systematic analysis of experimental material, trials with data\\
	\hline
	\multirow{2}{15 pt}{Group activities} & Participatory observation & Literature review, researchers knowledge\\
	\hline
	\end{tabular}
\end{table}
